A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-09 paper/paper.tex
Small edits

    Experimental results using two large graph databases show that \McSplit\ is
    more than an order of magnitude faster than the leading existing algorithms
    on instances involving undirected, unlabelled graphs, including the problem
    variant in which the subgraph must be connected.
\end{abstract}

@@

The most successful existing approaches to solving MCS are reformulation to the
maximum clique problem on one hand, and constraint programming
\cite{DBLP:conf/cp/McCreeshNPS16} on the other. In the clique
\textit{association graph} encoding, a graph is created with one node for each
pair in the set $\{(u,v) \mid u \in \V(G), v \in \V(H) \}$ and edges representing
pairs of mappings that may be chosen together. A maximum clique in this graph
represents a maximum common subgraph of $G$ and $H$.

>>>>

    Experimental results using two large graph databases show that \McSplit\ is
    more than an order of magnitude faster than the leading existing algorithms
    on undirected, unlabelled graphs, including the problem
    variant in which the subgraph must be connected.
\end{abstract}

@@

The most successful existing approaches to solving MCS are reformulation to the
maximum clique problem on one hand, and constraint programming
\cite{DBLP:conf/cp/McCreeshNPS16} on the other. In the clique
encoding, an \textit{association graph} is created with one node for each
pair in the set $\{(u,v) \mid u \in \V(G), v \in \V(H) \}$ and edges representing
pairs of mappings that may be chosen together. A maximum clique in this graph
represents a maximum common subgraph of $G$ and $H$.
